Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-05-31 ms.tex
added a few fixes details and clarifications about HDS spectra.

\begin{figure}
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec_interp.pdf}
\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec.pdf}
\caption{Example spectrum of \shStar\ near the Mg triplet.
{\it Top:} The full resolution original spectrum (blue) is compared to the Mg lines (black) to check wavelength solutions.
The points above a flux of 2.00 are marked as bad pixels and then linear interpolation is performed over these bad pixels to construct a cleaned spectrum (orange).
{\it Bottom} A convolution kernel is applied to the spectrum in order to compare to to HIGHRES models.
The HIGHRES model witha T=4500 K and log(g)=4.5 is a much closer match in terms of line ratios to the measured spectrum than the low surface gravity and higher temperature (3.9 $\pm$ 0.2, 4950 $\pm$ 50 K) reported in \citet{kawahara2013starspots}.}\label{fig:mgTriplet}
\end{centering}
\end{figure}

@@

We decided to re-visit the high resolution spectrum from \citet{kawahara2013starspots} by downloading the raw data from the Subaru SMOKA database.
We follow the \texttt{iraf} reduction techniques from the instrument manual\footnote{https://www.subarutelescope.org/Observing/Instruments/HDS/specana2014.10e.pdf}.
Some modifications to the manual were made, including a more aggressive -50/+50 lower and upper window for bad pixel identification with \texttt{mkbadpx} on the red CCD.
We applied bad pixel masks and bias files to each CCD separately.
Since \shStar\ is smaller than the background flux, we use a spectrum of KOI-678 (Kepler 211) to trace the spectrum and use this trace for \shStar.

\begin{figure}
\begin{centering}
\includegraphics[width=0.4\textwidth]{images/subaru/2013_vs_2015/out_HDSA00094087.pdf}
\includegraphics[width=0.4\textwidth]{images/subaru/2013_vs_2015/HDSA00111345.pdf}
\includegraphics[width=0.45\textwidth]{images/subaru/2013_vs_2015/profile_comparison.pdf}
\caption{Spectra images from 2013 versus 2015. The PSF profile (bottom panel) is much larger in 2013 is more difficult to fit with a tracing function.}\label{fig:mgTriplet}
\end{centering}
\end{figure}

The 2013 HDS data for \shStar\ display as very strange PSF, so we begin with the 2015 HDS data on the Subaru archive.
Figure \ref{fig:prof2013vs2015} shows an example blue-chip image from 2013 and 2015.
The wider longer slit (2 $\times$ 30 mm) used in 2013 versus the narrower one in 2015 produce very different PSFs.
The 2015 data has a much sharper PSF and and is easier to trace and calibrate without needing a brighter source for reference.
For wavelength identification, a Thorium Argon reference is used.
(Not to self:) The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas
The Th-Ar line identification was started with the atlas, rejecting high sigma points and then used to find the rest of the lines automatically.
The final fit was performed with a chebyshev polynomial, 4th order in x direction and 4th order in y direction.
The final rms in this wavelength solution is 0.0021 $\AA$.
After the reference spectrum is used to find a wavelength solution, the spectrum is examined some strong stellar lines, including the Na D$_1$/D$_2$ lines (Figure \ref{fig:naDlines} and the

@@

The region near the Mg triplet in Figure \ref{fig:mgTriplet} is a much closer match in terms of line ratios to the higher log(g) =4.5 and T=4500 K spectrum from HIGHRES.
The only mismatch between the 4500 K and log(g)=4.5 model and the HDS spectrum for \shStar\ is the overall line strengths.

\begin{figure}{!hbtp}
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/CaI6162_spec.pdf}
\caption{Example spectrum of \shStar\ near Ca I 6162 $\AA$, another gravity sensitive line.}\label{fig:mgTriplet}
\end{centering}
\end{figure}

>>>>

\begin{figure}
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec_interp.pdf}
\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec.pdf}
\caption{Example spectrum of \shStar\ near the Mg triplet.
{\it Top:} The full resolution original spectrum (blue) is compared to the Mg lines (black) to check wavelength solutions.
The points above a flux of 2.00 are marked as bad pixels and then linear interpolation is performed over these bad pixels to construct a cleaned spectrum (orange).
{\it Bottom} A convolution kernel is applied to the spectrum in order to compare to to HIGHRES models.
The HIGHRES model witha T=4500 K and log(g)=4.5 is a much closer match in terms of line ratios but not the strength of the features.}\label{fig:mgTriplet}
\end{centering}
\end{figure}

@@

We decided to re-visit the high resolution spectrum from \citet{kawahara2013starspots} by downloading the raw data from the Subaru SMOKA database.
We follow the \texttt{iraf} reduction techniques from the instrument manual\footnote{https://www.subarutelescope.org/Observing/Instruments/\\HDS/specana2014.10e.pdf}.
Some modifications to the manual were made, including a more aggressive -50/+50 lower and upper window for bad pixel identification with \texttt{mkbadpx} on the red CCD.
We applied bad pixel masks and bias files to each CCD separately.
Since \shStar\ is smaller than the background flux, we use a spectrum of KOI-678 (Kepler 211) to trace the spectrum and use this trace for \shStar.

\begin{figure}
\begin{centering}
\includegraphics[width=0.4\textwidth]{images/subaru/2013_vs_2015/out_HDSA00094087.pdf}
\includegraphics[width=0.4\textwidth]{images/subaru/2013_vs_2015/HDSA00111345.pdf}
\includegraphics[width=0.45\textwidth]{images/subaru/2013_vs_2015/profile_comparison.pdf}
\caption{Spectra images from 2013 versus 2015. The PSF profile (bottom panel) is much larger in 2013 is more difficult to fit with a tracing function.}\label{fig:prof2013vs2015}
\end{centering}
\end{figure}

The 2013 HDS data for \shStar\ display as very strange PSF, so we begin with the 2015 HDS data on the Subaru archive.
Figure \ref{fig:prof2013vs2015} shows an example blue-chip image from 2013 and 2015.
The wider longer slit (2 $\times$ 30 mm) used in 2013 versus the narrower one in 2015 (0.3 $\times$ 3.5 mm) produce very different PSFs.
The 2015 data has a much sharper PSF and and is easier to trace and calibrate without needing a brighter source for reference.
For wavelength identification, a Thorium Argon reference is used.
(Not to self:) The IRAF order 39 appears to be near 6370 $\AA$ to 6450 $\AA$ which is Order 95/Aperture 16 in the Subaru HDS Th-Ar atlas
The Th-Ar line identification was started with the atlas, rejecting high sigma points and then used to find the rest of the lines automatically.
The final fit was performed with a chebyshev polynomial, 4th order in x direction and 4th order in y direction.
The final rms in this wavelength solution is 0.0021 $\AA$.
After the reference spectrum is used to find a wavelength solution, the spectrum is examined some strong stellar lines, including the Na D$_1$/D$_2$ lines (Figure \ref{fig:naDlines} and the

@@

The region near the Mg triplet in Figure \ref{fig:mgTriplet} is a closer match in terms of line ratios to the higher log(g) =4.5 and T=4500 K spectrum from HIGHRES, but not the line strengths.

\begin{figure}[!hbtp]
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/CaI6162_spec.pdf}
\caption{Example spectrum of \shStar\ near Ca I 6162 $\AA$, another gravity sensitive line.}\label{fig:mgTriplet}
\end{centering}
\end{figure}
